A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2017-04-02 casm.tex
clear up which plots are from which experiment

%% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

@@

%% In this work we developed a model in order to have a better understanding of the
%% distribution of utility and trust in real networks of biomedical research
%% collaboration under certain social constraints  or topological properties.\\

@@

We ran two different experiments. In the first one we simulated different
values of carrying capacity $\nu$. With this experiment we were able
to see how the number of cooperators, utility, strength of interactions
among agents and the ratio of shifting state population would change
in the range of the carrying capacity. The states of the agents were
the same at initialization, for all values of the carrying
capacity. Since the model is deterministic, it will return the same
result if run under the same conditions.\\

The second experiment consisted in running the simulation under the
same degree of carrying capacity $\nu$ but randomizing the initial
states of the agents. This would show that the system converges to a
global state. For every network, the simulation was run 100 times and
results were averaged.

@@

\begin{figure} [h!]
\centering
\begin{tabular}{cc}
%   \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
%   \\
%   \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
\end{tabular}
\caption{Ratio of cooperators as a function of carrying capacity and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
}\label{CD}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
% \includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
\end{tabular}
\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
% \includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
\end{tabular}
\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{trust}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
% \includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
\end{tabular}
\caption{Shifting population between cooperators and defectors as a function of
carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_fitness.png} & 
% \includegraphics[scale=0.28]{images/watts_fitness.png} \\
% \includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
% \includegraphics[scale=0.28]{images/fosiss_fitness.png}
\end{tabular}
\caption{Utility distribution on different topologies. A. Random,
  Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network utility distribution is highly skewed
  to the right. C. Barab\'asi-Albert network utility is distributed highly
  skewed to the left. D. FOSISS, biomedical researchers collaboration network
  distribution of utility resembles that of the Barab\'asi-Albert
  network.}\label{histo_fitness} 
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_trust.png} & 
% \includegraphics[scale=0.28]{images/watts_trust.png} \\
% \includegraphics[scale=0.28]{images/barabasi_trust.png} & 
% \includegraphics[scale=0.28]{images/fosiss_trust.png}
\end{tabular}
\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
Barab\'asi-Albert network strength of interactions distribution is also a
normal-like curve. D. FOSISS, biomedical researchers collaboration network distribution of strength of interactions is skewed to the right.}\label{histo_trust}  
\end{figure}

@@

  FOSISS network is highly hierarchical according to its
  heterogeneity of $0.873$. Because of it, one would expect to find
  the presence of important hubs \cite{Wu:2008}, that is, a few
  researchers control the whole network, as has been reported in some
  other places \cite{yousefi-etal:2008}. Surprisingly, FOSISS network
  centralization is very low $0.023$, i.e. there are no researchers
  that centralize the majority of connections. Our guess is that the
  network is composed of many small communities or groups with a
  central researcher or Principal Investigator (PI). If this is the
  case in the FOSISS network, it means that those groups have a very
  hierarchical structure as well.\\

>>>>

% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

@@

@@

We ran two different experiments. In the First Experiment we simulated different
values of carrying capacity $\nu$. With this experiment we were able
to see how the number of cooperators, utility, strength of interactions
among agents and the ratio of shifting state population would change
in the range of the carrying capacity. The states of the agents were
the same at initialization, for all values of the carrying
capacity. Since the model is deterministic, it will return the same
result if run under the same conditions.\\

The Second Experiment consisted in running the simulation under the
same degree of carrying capacity $\nu$ but randomizing the initial
states of the agents. This would show that the system converges to a
global state. For every network, the simulation was run 100 times and
results were averaged.

@@

\begin{figure} [h!]
\centering
\begin{tabular}{cc}
%   \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
%   \\
%   \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
\end{tabular}
\caption{Ratio of cooperators as a function of carrying capacity and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.
}\label{CD}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/watts_fitness_nus_1.png} \\
% \includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_fitness_nus_1.png}
\end{tabular}
\caption{First Experiment's utility $U$ dynamics as a function of carrying capacity $\nu$ and time. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{fitness}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{images/watts_trust_nus_1.png} \\
% \includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_trust_nus_1.png}
\end{tabular}
\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{trust}
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{images/watts_state_nus.png} \\
% \includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{images/fosiss_state_nus.png}
\end{tabular}
\caption{Shifting population between cooperators and defectors as a function of
carrying capacity $\nu$ and time during First Experiment. Topologies are: A. Random, Erd\"{o}s-R\'enyi. B. Watts-Strogatz. C. Barab\'asi-Albert. D. FOSISS.}\label{state} 
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_fitness.png} & 
% \includegraphics[scale=0.28]{images/watts_fitness.png} \\
% \includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
% \includegraphics[scale=0.28]{images/fosiss_fitness.png}
\end{tabular}
\caption{Second Experiment's utility distribution on different topologies. A. Random,
  Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network utility distribution is highly skewed
  to the right. C. Barab\'asi-Albert network utility is distributed highly
  skewed to the left. D. FOSISS, biomedical researchers collaboration network
  distribution of utility resembles that of the Barab\'asi-Albert
  network.}\label{histo_fitness} 
\end{figure}

@@

% \includegraphics[scale=0.28]{images/erdos_trust.png} & 
% \includegraphics[scale=0.28]{images/watts_trust.png} \\
% \includegraphics[scale=0.28]{images/barabasi_trust.png} & 
% \includegraphics[scale=0.28]{images/fosiss_trust.png}
\end{tabular}
\caption{Strength of interactions distribution on different topologies during Second Experiment. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
Barab\'asi-Albert network strength of interactions distribution is also a
normal-like curve. D. FOSISS, biomedical researchers collaboration network distribution of strength of interactions is skewed to the right.}\label{histo_trust}  
\end{figure}

@@

  FOSISS network is highly hierarchical according to its
  heterogeneity of $0.873$. Because of it, one would expect to find
  the presence of important hubs \cite{Wu:2008}, that is, a few
  researchers control the whole network, as has been reported in some
  other places \cite{Yousefi-etal:2008}. Surprisingly, FOSISS network
  centralization is very low $0.023$, i.e. there are no researchers
  that centralize the majority of connections. Our guess is that the
  network is composed of many small communities or groups with a
  central researcher or Principal Investigator (PI). If this is the
  case in the FOSISS network, it means that those groups have a very
  hierarchical structure as well.\\
